---
title: "Google Trends Analysis"
author: "Emily Halford"
date: "9/26/2020"
output: html_document
---

## Loading Packages

The following code loads the tidyverse and gtrendsR packages, as well as creating a connection to the "functions" script and loading the contained functions.

```{r packages}

library(tidyverse)
library(gtrendsR)
library(bcp)
source("./functions.R")

```

## Pulling in data

The following code pulls some Google Trends data for "Supreme Court" searches. We will use this dataset with our functions below.

```{r data_pull}

data = gtrends(keyword = "supreme court", geo = "US", time = "today 1-m")$interest_over_time %>% 
  mutate(
    date = as.Date(date)
  )

```

## Using functions

Now we just apply the functions that were created in the "functions" script to run a very simple changepoint analysis.

```{r functions}

google_graph(data, data$date, data$hits, 'Google Searches for "Supreme Court"')

bcp_dataframe = bcp_analysis(data$hits, data)

bcp_plot(bcp_dataframe)

```

